Temporal stability in human interaction networks: sector sizes, topological prominence and time activity (Supporting Information document)

### 2015-10-15 paper.tex
pequena homogeneizacao das tabelas
arrumada notacao das medidas circulares

\noindent
Also, the ratio $r=\frac{b_l}{b_h}$ between the lowest and the highest incidences on the histograms 
served as a further clue of how close the distribution was to being uniform.
As expected, a positive correlation was found in all $r, Var(z)$, $S(z)$ and $\delta(z)$ dispersion measures,
which can be noticed in the Section~\ref{si:circ} of the Supporting Information document.
The circular dispersion $\delta(z)$ was found more sensitive and therefore preferred 
in the discussion of results.

@@

\begin{table}
	\caption{The rescaled circular mean $\theta_\mu'$ and the circular dispersion $\delta(z)$, described in Section~\ref{sec:mtime}, for different timescales.
		This example table was constructed using all LAD messages, and the results are the same for other lists, as shown in Section~\ref{si:circ} of the Supporting Information document.
	The most uniform distribution of activity was found in seconds and minutes.
	Hours of the day exhibited the most concentrated activity (lowest $\delta(z)$), with mean between 14h and 15h ($\theta'=-9.61$).
	Weekdays, month days and months have mean near zero (i.e. near the beginning of the week, month and year) and high dispersion.}
	\begin{center}
		\begin{tabular}{ |l|| c|c| }
			\hline
			%scale & $\theta_\mu'$ & $S(z)$ & $Var(z)$ & $\delta(z)$ & $\frac{max(incidence)}{min(incidence)}$ & $ \mu_{\frac{max(incidence')}{min(incidence')}} $ & $ \sigma_{\frac{max(incidence')}{min(incidence')} } $ \\ \hline\hline
			%& $\theta_\mu'$ & $S(z)$ & $Var(z)$ & $\delta(z)$  \\ \hline\hline
			{\bf scale} & {\bf mean} \boldsymbol{$\theta_\mu'$} & {\bf dispersion} \boldsymbol{$\delta(z)$ }  \\ \hline\hline
			\input{tables/tab2TimeLAD___}
		\end{tabular}
	\end{center}
	\label{tab:circ}
\end{table}

@@

\begin{table}
	\caption{Activity percentages along the days of the week.
	Higher activity was observed during weekdays, with a decrease of activity on weekends of at least one third and two thirds in extreme cases.}
	\begin{center}
		\begin{tabular}{ | l |  c | c | c | c | c |   c | c |}
			\hline
			& Mon & Tue & Wed & Thu & Fri & Sat & Sun  \\ \hline
			\input{tables/tabWeekdays}
		\end{tabular}
	\end{center}
	\label{tab:win}
\end{table}
For example, uniform activity is found with respect to seconds, minutes and days of the months,
weekend days exhibit about half the activity of regular weekdays,
and there is a peak of activity between 11am and 12pm.

>>>>

\noindent
Also, the ratio $r=\frac{b_l}{b_h}$ between the lowest $b_l$ and the highest $b_h$ incidences on the histograms 
served as a further clue of how close the distribution was to being uniform.
As expected, a positive correlation was found in all $r, Var(z)$, $S(z)$ and $\delta(z)$ dispersion measures,
which can be noticed in the Section~\ref{si:circ} of the Supporting Information document.
The circular dispersion $\delta(z)$ was found more sensitive and therefore preferred 
in the discussion of results.

@@

\begin{table}
	\caption{The rescaled circular mean $\theta_\mu'$ and the circular dispersion $\delta(z)$, described in Section~\ref{sec:mtime}, for different timescales.
		This example table was constructed using all LAD messages, and the results are the same for other lists, as shown in Section~\ref{si:circ} of the Supporting Information document.
	The most uniform distribution of activity was found in seconds and minutes.
	Hours of the day exhibited the most concentrated activity (lowest $\delta(z)$), with mean between 14h and 15h ($\theta'=-9.61$).
	Weekdays, month days and months have mean near zero (i.e. near the beginning of the week, month and year) and high dispersion.}
	\begin{center}
		\begin{tabular}{ |l|| c|c| }
			\hline
			%scale & $\theta_\mu'$ & $S(z)$ & $Var(z)$ & $\delta(z)$ & $\frac{max(incidence)}{min(incidence)}$ & $ \mu_{\frac{max(incidence')}{min(incidence')}} $ & $ \sigma_{\frac{max(incidence')}{min(incidence')} } $ \\ \hline\hline
			%& $\theta_\mu'$ & $S(z)$ & $Var(z)$ & $\delta(z)$  \\ \hline\hline
			scale & mean $\theta_\mu'$ & dispersion $\delta(z)$  \\ \hline
			\input{tables/tab2TimeLAD___}
		\end{tabular}
	\end{center}
	\label{tab:circ}
\end{table}

@@

\begin{table}
	\caption{Activity percentages along the days of the week.
	Higher activity was observed during weekdays, with a decrease of activity on weekends of at least one third and two thirds in extreme cases.}
	\begin{center}
		\begin{tabular}{ | l ||  c | c | c | c | c |   c | c |}
			\hline
			& Mon & Tue & Wed & Thu & Fri & Sat & Sun  \\ \hline
			\input{tables/tabWeekdays}
		\end{tabular}
	\end{center}
	\label{tab:win}
\end{table}
For example, uniform activity is found with respect to seconds, minutes and days of the months,
weekend days exhibit about half the activity of regular weekdays,
and there is a peak of activity between 11am and 12pm.

### 2015-10-15 supportingInformation.tex
arrumada notacao das medidas circulares

\subsection{Time circular measures}\label{si:circ}
The metrics with which we report measurements and results
of activity along time are the rescaled circular mean $\theta_\mu'$,
the standard deviation $S(z)$, the variance $Var(z)$, the circular dispersion $\delta(z)$
and the relation between the minimum and the maximum incidences $\frac{min(incidence)}{max(incidence)}$ at each time scale.
Also, the mean $ \mu_{\frac{min(incidence')}{max(incidence')}} $ and 
the standard deviation $ \sigma_{\frac{min(incidence')}{max(incidence')} }$ 
of the relation between the minimum and the maximum incidences
are given for 1000 uniform distribution simulations within the 
same number of bins and with the same number of samples~\footnote{Numpy version 1.8.2, ``random.randint'' function, was used for simulations, algorithms in \url{https://pypi.python.org/pypi/gmane}}.
Greater dispersion is found on the scales of seconds and minutes, followed
by days of the month.
Greater localization is found in the scale of hours of the day, followed by weekdays and months.

\begin{table*}[!h]
	\caption{LAU circular measurements.}
\begin{center}
    \begin{tabular}{ |l|| c|c|c|c|c||c|c| }
        \hline
scale & $\theta_\mu'$ & $S(z)$ & $Var(z)$ & $\delta(z)$ & $\frac{min(incidence)}{max(incidence)}$ & $ \mu_{\frac{min(incidence')}{max(incidence')}} $ & $ \sigma_{\frac{min(incidence')}{max(incidence')} } $ \\ \hline\hline
	\input{tables/tab2TimeLAU}
    \end{tabular}
\end{center}
\label{tab:circLau}
\end{table*}
\begin{table*}[!h]
	\caption{LAD circular measurements.}
\begin{center}
    \begin{tabular}{ |l|| c|c|c|c|c||c|c| }
        \hline
scale & $\theta_\mu'$ & $S(z)$ & $Var(z)$ & $\delta(z)$ & $\frac{min(incidence)}{max(incidence)}$ & $ \mu_{\frac{min(incidence')}{max(incidence')}} $ & $ \sigma_{\frac{min(incidence')}{max(incidence')} } $ \\ \hline\hline
	\input{tables/tab2TimeLAD}
    \end{tabular}
\end{center}
\label{tab:circLad}
\end{table*}
\begin{table*}[!h]
	\caption{MET circular measurements.}
\begin{center}
    \begin{tabular}{ |l|| c|c|c|c|c||c|c| }
        \hline
scale & $\theta_\mu'$ & $S(z)$ & $Var(z)$ & $\delta(z)$ & $\frac{min(incidence)}{max(incidence)}$ & $ \mu_{\frac{min(incidence')}{max(incidence')}} $ & $ \sigma_{\frac{min(incidence')}{max(incidence')} } $ \\ \hline\hline
	\input{tables/tab2TimeMET}
    \end{tabular}
\end{center}
\label{tab:circMet}
\end{table*}
\begin{table*}[!h]
	\caption{CPP circular measurements.}
\begin{center}
    \begin{tabular}{ |l|| c|c|c|c|c||c|c| }
        \hline
scale & $\theta_\mu'$ & $S(z)$ & $Var(z)$ & $\delta(z)$ & $\frac{min(incidence)}{max(incidence)}$ & $ \mu_{\frac{min(incidence')}{max(incidence')}} $ & $ \sigma_{\frac{min(incidence')}{max(incidence')} } $ \\ \hline\hline
	\input{tables/tab2TimeCPP}
    \end{tabular}
\end{center}
\label{tab:circCPP}
\end{table*}

>>>>

\subsection{Time circular measures}\label{si:circ}
The metrics with which we report measurements and results
of activity along time are the rescaled circular mean $\theta_\mu'$,
the standard deviation $S(z)$, the variance $Var(z)$, the circular dispersion $\delta(z)$
and the ration between the lowest $b_l$ and the highest $b_h$ incidences $\frac{b_l}{b_h}$ at each time scale.
Also, the mean $\mu_{\frac{b_l'}{b_h'}}$ and 
the standard deviation $\sigma_{\frac{b_l'}{b_h'}}$ 
of the relation between the minimum $b_l'$ and the maximum $b_h'$ incidences
are given for 1000 uniform distribution simulations within the 
same number of bins and with the same number of samples~\footnote{Numpy version 1.8.2, ``random.randint'' function, was used for simulations, algorithms in \url{https://pypi.python.org/pypi/gmane}}.
Greater dispersion is found on the scales of seconds and minutes, followed
by days of the month.
Greater localization is found in the scale of hours of the day, followed by weekdays and months.

\begin{table*}[!h]
	\caption{LAU circular measurements.}
\begin{center}
    \begin{tabular}{ |l|| c|c|c|c|c||c|c| }
        \hline
scale & $\theta_\mu'$ & $S(z)$ & $Var(z)$ & $\delta(z)$ & $\frac{b_l}{b_h}$ & $ \mu_{\frac{b_l'}{b_h'}} $ & $ \sigma_{\frac{b_l'}{b_h'}} $ \\ \hline\hline
	\input{tables/tab2TimeLAU}
    \end{tabular}
\end{center}
\label{tab:circLau}
\end{table*}
\begin{table*}[!h]
	\caption{LAD circular measurements.}
\begin{center}
    \begin{tabular}{ |l|| c|c|c|c|c||c|c| }
        \hline
scale & $\theta_\mu'$ & $S(z)$ & $Var(z)$ & $\delta(z)$ & $\frac{b_l}{b_h}$ & $ \mu_{\frac{b_l'}{b_h'}} $ & $ \sigma_{\frac{b_l'}{b_h'}} $ \\ \hline\hline
	\input{tables/tab2TimeLAD}
    \end{tabular}
\end{center}
\label{tab:circLad}
\end{table*}
\begin{table*}[!h]
	\caption{MET circular measurements.}
\begin{center}
    \begin{tabular}{ |l|| c|c|c|c|c||c|c| }
        \hline
scale & $\theta_\mu'$ & $S(z)$ & $Var(z)$ & $\delta(z)$ & $\frac{b_l}{b_h}$ & $ \mu_{\frac{b_l'}{b_h'}} $ & $ \sigma_{\frac{b_l'}{b_h'}} $ \\ \hline\hline
	\input{tables/tab2TimeMET}
    \end{tabular}
\end{center}
\label{tab:circMet}
\end{table*}
\begin{table*}[!h]
	\caption{CPP circular measurements.}
\begin{center}
    \begin{tabular}{ |l|| c|c|c|c|c||c|c| }
        \hline
scale & $\theta_\mu'$ & $S(z)$ & $Var(z)$ & $\delta(z)$ & $\frac{b_l}{b_h}$ & $ \mu_{\frac{b_l'}{b_h'}} $ & $ \sigma_{\frac{b_l'}{b_h'}}$ \\ \hline\hline
	\input{tables/tab2TimeCPP}
    \end{tabular}
\end{center}
\label{tab:circCPP}
\end{table*}
